Fusion Moves for Correlation Clustering

### 2014-10-30 paper/egpaper_for_review.tex
w.i.p.

% If you comment hyperref and then uncomment it, you should delete
% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
% run, let it finish, and you should be clear).
\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}

\def\arraystretch{0.8}
\renewcommand{\tabcolsep}{2pt}
\newcommand{\thickline}{2pt}
\newcommand{\scatterplotpath}{./scatterplots/}

@@

\begin{center}
    \begin{eqnarray}
        l^* &=& \argmin_{L \in \{1,\ldots,|V|\}^{|V|}} \sum_{ (i,j) \in E } w_{ij} \cdot [l_{u} \neq l_{v}] \label{eq:nodeproblem}\\
   %     y_{ij}^* &=& [l_{u} \neq l_{v}] 
        y^* &=& \argmin_{y \in MC(G)\cap \{0,1\}^{|E|}} \sum_{ (i,j) \in E } w_{ij} \cdot y_{ij} \label{eq:edgeproblem}%\\ 
    \end{eqnarray}
\end{center}

@@

\input{inputs/fig_alg_graph.tex}

\subsection{Define Fusion on Segmentations}
\input{inputs/fig_move_graph.tex}

Global optimal solvers for multicut do not scale beyond ??? \cite{???}.
Good approximate solvers for planar graphs exist \cite{beier_2014_cvpr,yarkony_2012_eccv} 
but have difficulties to find good solutions for non planar graphs \cite{beier_2014_cvpr}.
%
To make multicuts scalable, it is desirable to replace the graph $G$
with a graph $\hat{G}$, which is smaller in the number of nodes and edges. 
If $\hat{G}$ is small enough, it is feasible to use global optimal solvers.
%
A trivial way to reduce the size of the graph  is edge contraction.
Until a desirable size is reached, one might contract the edge with
the highest weight. A cut on the contracted graph  $\hat{G}$ is always
a valid cut on $\hat{G}$.
%
On the other hand, if an edge $e$ is contracted, it will never be cut.
If $e$ is part of the cut in a global optimal solution, we cannot find
this cut.
%
To overcome this problem  we can randomize the edge contraction,
and repeat this multiple times and remember the best solution.
%
But this would throw away all the ``not the best'' solutions (rewrite me).
Within this work we propose the following nifty trick.
Instead of throwing away solutions, we intersect them with the 
best solution, and solve the multicut on the resulting
graph.
Therefore we fuse multiple solutions,

\begin{algorithm}
\begin{scriptsize}
\caption{Fusion Based Algorithms}\label{alg:fusion}
\begin{algorithmic}[1]
\Procedure{Intersection-Based-Inference}{GEN,$J$,$X$}
\State $x^0 \gets \textrm{initial state form } X$
\State $n \gets 0 $                                 \Comment{Number of moves}
\State $m \gets 0 $                                 \Comment{Number of moves without progress}
\While{$m < m_{\max}$ and $n < n_{\max}$ }
\State $n \gets n+1$ 
 \State $x'\gets GEN(x^{n-1},J,X)$                    \Comment{Generate proposal}
 \If{$J(x^{n-1}) \leq J(x')$}                       
   \State $x^{n} \gets Fuse(x^{n-1},x',J)$             
 \Else
   \State $x^{n} \gets Fuse(x',x^{n-1},J)$
 \EndIf
 \If{$J(x^{n}) \leq J(x^{n-1})$}
   \State $m \gets 0$                                 \Comment{Reset counter}
 \Else
   \State $m \gets m+1$                               \Comment{Increment counter}
 \EndIf
\EndWhile
\State \textbf{return} $x^n$
\EndProcedure
\end{algorithmic}
\end{scriptsize}
\end{algorithm}

@@

@@

\begin{remark}[Fix-point]
Let $Y$ be the set of possible proposals, than
$y'$ is a fix-point if $y'=\arg\max_{y\in P(G_{y'\OR y''})} y\cdot w$ for all $y''\in Y$
\end{remark}

>>>>

% If you comment hyperref and then uncomment it, you should delete
% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
% run, let it finish, and you should be clear).
\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}
\usepackage{bm}% ändert \boldsymbol
\def\arraystretch{0.8}
\renewcommand{\tabcolsep}{2pt}
\newcommand{\thickline}{2pt}
\newcommand{\scatterplotpath}{./scatterplots/}

@@

\begin{center}
    \begin{eqnarray}
        l^* &=& \argmin_{L \in \{1,\ldots,|V|\}^{|V|}} \sum_{ (i,j) \in E } w_{ij} \cdot [l_{i} \neq l_{j}] \label{eq:nodeproblem}\\
   %     y_{ij}^* &=& [l_{u} \neq l_{v}] 
        y^* &=& \argmin_{y \in MC(G)\cap \{0,1\}^{|E|}} \sum_{ (i,j) \in E } w_{ij} \cdot y_{ij} \label{eq:edgeproblem}%\\ 
    \end{eqnarray}
\end{center}

@@

%\input{inputs/fig_alg_graph.tex}

\subsection{Define Fusion on Segmentations}

Given two proposal solutions $y'$ and $y''$
the fusion move between those solutions is defined
as follows:

Let the $\bar{y}$ be the edge wise or of  $y'$ and $y''$.
\begin{equation}
\breve{y} =  y' \cup y''.
\end{equation}
Contraction of all edges in $G$ where $\bar{y}=0$ defines
a smaller graph $G_{\bar{y}}$ and the corresponding
edge weights $W_{\hat{y}}$.
Any cut $\bar{y}$ on $G_{\hat{y}}$ induces a cut $y$ on $G$.
The function 
$\rho_y^{-1}$ maps a cut from $G_{\hat{y}}$  to $G$

\begin{equation}
   \rho_y^{-1} : P(G_y) \to P(G)
\end{equation}

Therefore solving eq. \ref{eq:edgeproblem} 
on $G_{\hat{y}}$
leads to a cut on $G$ which is guaranteed to 
to have a better or equal energy
then any of the two proposal solutions.

\input{inputs/fig_move_graph.tex}

% Global optimal solvers for multicut do not scale beyond ??? \cite{???}.
% Good approximate solvers for planar graphs exist \cite{beier_2014_cvpr,yarkony_2012_eccv} 
% but have difficulties to find good solutions for non planar graphs \cite{beier_2014_cvpr}.

% To make multicuts scalable, it is desirable to replace the graph $G$
% with a graph $\hat{G}$, which is smaller in the number of nodes and edges. 
% If $\hat{G}$ is small enough, it is feasible to use global optimal solvers.

% A trivial way to reduce the size of the graph  is edge contraction.
% Until a desirable size is reached, one might contract the edge with
% the highest weight. A cut on the contracted graph  $\hat{G}$ is always
% a valid cut on $\hat{G}$.

% On the other hand, if an edge $e$ is contracted, it will never be cut.
% If $e$ is part of the cut in a global optimal solution, we cannot find
% this cut.

% To overcome this problem  we can randomize the edge contraction,
% and repeat this multiple times and remember the best solution.

% But this would throw away all the ``not the best'' solutions (rewrite me).
% Within this work we propose the following nifty trick.
% Instead of throwing away solutions, we intersect them with the 
% best solution, and solve the multicut on the resulting
% graph.
% Therefore we fuse multiple solutions,

\begin{algorithm}
\begin{scriptsize}
\caption{Fusion Based Algorithms}\label{alg:fusion}

\begin{algorithmic}[1]
\Procedure{Intersection-Based-Inference}{GEN,$J$,$X$}
\State $x^0 \gets \textrm{initial state form } X$
\State $n \gets 0 $                                 \Comment{Number of moves}
\State $m \gets 0 $                                 \Comment{Number of moves without progress}
\While{$m < m_{\max}$ and $n < n_{\max}$ }
\State $n \gets n+1$ 
 \State $x'\gets GEN(x^{n-1},J,X)$                    \Comment{Generate proposal}
 \If{$J(x^{n-1}) \leq J(x')$}                       
   \State $x^{n} \gets Fuse(x^{n-1},x',J)$             
 \Else
   \State $x^{n} \gets Fuse(x',x^{n-1},J)$
 \EndIf
 \If{$J(x^{n}) \leq J(x^{n-1})$}
   \State $m \gets 0$                                 \Comment{Reset counter}
 \Else
   \State $m \gets m+1$                               \Comment{Increment counter}
 \EndIf
\EndWhile
\State \textbf{return} $x^n$
\EndProcedure
\end{algorithmic}
\end{scriptsize}
\end{algorithm}

@@

\begin{center}
    \begin{eqnarray}
        y 
        &=& 
        \rho_{\hat{y}}^{-1}(
        \argmin_{y \in MC(G_{\hat{y}})\cap \{0,1\}^{|E_{\hat{y}}|}} 
        \sum_{ (i,j) \in E_{\hat{y}} } 
        w^{\hat{y}}_{ij} \cdot \bar{y}_{ij} 
    \end{eqnarray}
\end{center}

\begin{center}
    \begin{eqnarray}
      y \cdot w \leq \min(y'\cdot w,  y'' \cdot w) 
    \end{eqnarray}
\end{center}

@@

\begin{remark}[Fix-point (pointless to me)]
Let $Y$ be the set of possible proposals, than
$y'$ is a fix-point if $y'=\arg\max_{y\in P(G_{y'\OR y''})} y\cdot w$ for all $y''\in Y$
\end{remark}
